---
title: "tmesig documentation"
output: html_document
date: '2022-07-13'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo=F, message=F, warning=F}
library(tidyverse)
library(flextable)
```
## Z Score Calculations

### calculate_avg_z_score
`calculate_avg_z_score` is a function that takes a data frame and calculates the average z score for all the values in a given data set

```{r calculateAvgZScore, eval=F}
calculateAvgZScore(gene_matrix = expressions, gene_list = c("RNF43","BMP4","TSPAN8","PPP1R1B","SLC44A4","C9orf152","VWA2","AXIN2","SP5","NKD1","CFTR","LGR5","ODAM"))
```

### geneEntries
`geneEntries` contains genes within vectors which are signatures

```{r geneEntries, eval=F}
geneEntries("IFNg_18")
```


`calculate_avg_z_score` can be used with `gene_entires` to pull signatures
```{r calculate_avg_z_score2, eval=F}
calculate_avg_z_score(gene_matrix = expressions, gene_list = gene_entries("IFNg_18"))
```

### Table of Signatures
The table below includes each of the signatures along that we have implemented into the geneEntries function

```{r, eval=T, echo=F, warning=F}
library(readxl)
Gene_signatures <- read_excel("../Data/Gene_signatures.xlsx", sheet = "Full-Sheet") 
Gene_signatures %>% flextable()
```
